\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-27 tex/ms.tex
bla bla...

In general, we find that the iterative scheme converges within about 50 
iterations, taking about fifteen minutes on a laptop computer. However, since it 
is strongly regularized, the model significantly
underfits the data. In the second step, we remove our L2 prior on the spherical
harmonic coefficients and instead regularize the actual surface albedo, which
we compute on a uniform spherical grid with 50,000 points. We enforce a 
uniform prior in the range $[0, 1]$, with a small amount of Gaussian smoothing on either 
side. We additionally impose a constraint on the power spectrum of the
inferred map, requiring that it be drawn from a distribution whose mean
is a decaying power law in the spherical harmonic degree $l$ in order
to suppress ringing and spurious high order features.
Our full negative log likelihood function in this step is therefore
%
\begin{align}
    \label{eq:nll}
    -\log\mathcal{L} \, = \, 
        &\frac{1}{2}(\mathbf{f} - \mathbf{m})^\top \boldsymbol{\Sigma}^{-1} (\mathbf{f} - \mathbf{m}) \, + \nonumber \\
        &\frac{1}{2}\mathbf{w}^\top \boldsymbol{\Lambda}_w^{-1} \mathbf{w} \, + \nonumber \\
        &\frac{1}{2}(\mathbf{a_-} + 1 - \mathbf{a_+})^\top \boldsymbol{\Lambda}_a^{-1} (\mathbf{a_-} + 1 - \mathbf{a_+}) \, + \nonumber \\
        &\frac{1}{2}(\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma})^\top \boldsymbol{\Lambda}_\rho^{-1} (\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma}) \, + \nonumber \\
        &\frac{1}{2} \frac{(\gamma - \gamma_0)^2}{\sigma_\gamma^2}
        \quad,
\end{align}
%
where $\mathbf{f}$ is the measured flux across all targets,
$\mathbf{m}$ is the full model (Equation~\ref{eq:model}),
$\boldsymbol{\Sigma}$ is the (diagonal) data covariance, 
$\mathbf{w}$ are the systematics model weights for all targets,
$\boldsymbol{\Lambda}_w$ is the prior covariance of the weights
(Equation~\ref{eq:wprior}), $\mathbf{a_-}$ and $\mathbf{a_+}$ are
vectors containing the values of the albedo that are below zero and above one, 
respectively, $\boldsymbol{\Lambda}_a$ is the covariance of the Gaussian
used to smooth the edges of the top-hat prior on $\mathbf{a}$,
$\boldsymbol{\rho}$ is the power spectrum of the inferred spherical harmonic map
(equal to the sum of the squares of the coefficients at each degree $\boldsymbol{l}$),
$\gamma$ is the power law index of the power spectrum prior, $\boldsymbol{\Lambda}_\rho$ is the
covariance of that prior, $\gamma_0 = 1.5$ is the mean of the prior on $\gamma$
and $\sigma_\gamma^2 = 10^{-2}$ is the corresponding variance.
%
For simplicity, all our prior covariances are diagonal and
homoscedastic with variances equal to $2.5\times 10^{-3}$ for $\mathbf{w}$, and
$10^{-8}$ for $\mathbf{a}$, $10^{-1}$ for $\boldsymbol{\rho}$.

Unfortunately, the constraints outlined above break the linearity 
of the problem, and we must turn to a non-linear optimizer. We use the 
\textsf{AdamOptimizer} method in the \tf package \citep{Abadi2015}
to maximize Equation~(\ref{eq:nll}). Starting with the values of the
weights obtained in the first step, we run the \textsf{AdamOptimizer}
for 1000 iterations, well past convergence. Since \tf automatically
computes and propagates gradient information, this step is fast
and also finishes in under five minutes on a standard computer.

@@

Figure~\ref{fig:map_L2} shows the maximum likelihood map inferred
during the first stage of our optimization procedure. Since the map
coefficients were heavily regularized, the dynamic range of the albedo
variations was less than 10\%; we scaled it to span the range [0, 1]
for better visualization. Furthermore, although the resolution is on 
the order of $12^\circ$, features typically span ${\sim}45^\circ$; this is
also an artefact of our regularization. However, broad features are already
visible in the map: three bright regions and two dark regions (one of which
wraps around the antimeridian). Overplotted on the inferred map are
coastal outlines corresponding to our current best understanding of 
the geography of Sol d. One can see that the three bright regions roughly
track, from left to right, continents we shall refer to as ``South America,''
``Africa,'' and ``Asia,'' in keeping with the literature. The dark regions
are associated with the two major purported oceans on the planet, the
``Pacific'' (centered at longitude $\pm180^\circ$) and ``Atlantic''
(centered at longitude $\-45^\circ$).

@@

@@

In fact, because of these points, there should formally be \emph{no} null space 
in this particular problem. In practice, however, it is evident from
Figure~\ref{fig:map} that degenaricies still abound. \todo{bla bla bla.}

\subsection{Temporal Evolution}

@@

\subsection{Sources of Bias}

@@

\todo{(comparison of inferred features to ``model'' (Earth))}

\todo{No zonal cloud bands: prior.}

>>>>

In general, we find that the iterative scheme converges within about 50 
iterations, taking about three minutes on a laptop computer. However, since it 
is strongly regularized, the model significantly
underfits the data. In the second step, we remove our L2 prior on the spherical
harmonic coefficients and instead regularize the actual surface albedo, which
we compute on a uniform spherical grid with 50,000 points. We enforce a 
uniform prior in the range $[0, 1]$, with a small amount of Gaussian smoothing on either 
side. We additionally impose a constraint on the power spectrum of the
inferred map, requiring that it be drawn from a distribution whose mean
is a decaying power law in the spherical harmonic degree $l$ in order
to suppress ringing and spurious high order features.
Our full negative log likelihood function in this step is therefore
%
\begin{align}
    \label{eq:nll}
    -\log\mathcal{L} \, = \, 
        &\frac{1}{2}(\mathbf{f} - \mathbf{m})^\top \boldsymbol{\Sigma}^{-1} (\mathbf{f} - \mathbf{m}) \, + \nonumber \\
        &\frac{1}{2}\mathbf{w}^\top \boldsymbol{\Lambda}_w^{-1} \mathbf{w} \, + \nonumber \\
        &\frac{1}{2}(\mathbf{a_-} + 1 - \mathbf{a_+})^\top \boldsymbol{\Lambda}_a^{-1} (\mathbf{a_-} + 1 - \mathbf{a_+}) \, + \nonumber \\
        &\frac{1}{2}(\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma})^\top \boldsymbol{\Lambda}_\rho^{-1} (\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma}) \, + \nonumber \\
        &\frac{1}{2} \frac{(\gamma - \gamma_0)^2}{\sigma_\gamma^2}
        \quad,
\end{align}
%
where $\mathbf{f}$ is the measured flux across all targets,
$\mathbf{m}$ is the full model (Equation~\ref{eq:model}),
$\boldsymbol{\Sigma}$ is the (diagonal) data covariance, 
$\mathbf{w}$ are the systematics model weights for all targets,
$\boldsymbol{\Lambda}_w$ is the prior covariance of the weights
(Equation~\ref{eq:wprior}), $\mathbf{a_-}$ and $\mathbf{a_+}$ are
vectors containing the values of the albedo that are below zero and above one, 
respectively, $\boldsymbol{\Lambda}_a$ is the covariance of the Gaussian
used to smooth the edges of the top-hat prior on $\mathbf{a}$,
$\boldsymbol{\rho}$ is the power spectrum of the inferred spherical harmonic map
(equal to the sum of the squares of the coefficients at each degree $\boldsymbol{l}$),
$\gamma$ is the power law index of the power spectrum prior, $\boldsymbol{\Lambda}_\rho$ is the
covariance of that prior, $\gamma_0 = 1.5$ is the mean of the prior on $\gamma$
and $\sigma_\gamma^2 = 10^{-2}$ is the corresponding variance.
%
For simplicity, all our prior covariances are diagonal and
homoscedastic with variances equal to $2.5\times 10^{-3}$ for $\mathbf{w}$, and
$10^{-8}$ for $\mathbf{a}$, $10^{-1}$ for $\boldsymbol{\rho}$.

Unfortunately, the constraints outlined above break the linearity 
of the problem, and we must turn to a non-linear optimizer. We use the 
\textsf{AdamOptimizer} method in the \tf package \citep{Abadi2015}
to maximize Equation~(\ref{eq:nll}). Starting with the values of the
weights obtained in the first step, we run the \textsf{AdamOptimizer}
for 1000 iterations, well past convergence. Since \tf automatically
computes and propagates gradient information, this step is fast
and also finishes in under three minutes on a laptop.

@@

Figure~\ref{fig:map_L2} shows the maximum likelihood map inferred
during the first stage of our optimization procedure. Since the map
coefficients were heavily regularized, the dynamic range of the albedo
variations was less than 10\%; we scaled it to span the range [0, 1]
for better visualization. Furthermore, although the resolution is on 
the order of $18^\circ$, features typically span ${\sim}45^\circ$; this is
also an artefact of our regularization. However, broad features are already
visible in the map: three bright regions and two dark regions (one of which
wraps around the antimeridian). Overplotted on the inferred map are
coastal outlines corresponding to our current best understanding of 
the geography of Sol d. One can see that the three bright regions roughly
track, from left to right, continents we shall refer to as ``South America,''
``Africa,'' and ``Asia,'' in keeping with the literature. The dark regions
are associated with the two major purported oceans on the planet, the
``Pacific'' (centered at longitude $\pm180^\circ$) and ``Atlantic''
(centered at longitude $\-45^\circ$).

@@

\subsection{An Ill-Posed Problem}
\label{sec:illposed}

@@

In fact, because of these points, there should formally be \emph{no} null space 
in this particular problem. In practice, however, it is evident from
Figure~\ref{fig:map} that degenaricies still abound. This is likely because
of the finite signal-to-noise of our measurements and various biases in
our adopted model. While the measurement errors on our data points are
quite small---since the signal of Sol d is both quite strong and independently
measured at 95 different positions on the detector---our lack of understanding
of the complex optics that give rise to the signal in the first place, and our
attempt to na{\"i}vely model it with pixel-level decorrelation, likely
introduces significant correlated noise into the problem. We discuss
sources of bias in more detail in \S\ref{sec:bias} below

\subsection{Confirmation Bias}
\label{sec:confirmation}
\todo{bla bla bla}

\subsection{Temporal Evolution}
\label{sec:temporal}

@@

\subsection{Sources of Bias}
\label{sec:bias}

\todo{PLD, moon background, etc.}

@@

\subsection{Application to Other Planets}
\label{sec:otherplanets}

\todo{For realz, how would we do this.}
